---
title: "Final Report for Intro to Data Science"
output: html_notebook
Name: "Kyle Murphy"
---

**How healthy is Starbucks?**

**Project Author**

Kyle Murphy

**Introduction**

Starbucks has become something of a global phenomenon with how many people order Starbucks everyday. The question no one seems to be asking is what are the nutritional values of your favorite Starbucks drinks. As well as what category of Starbucks beverages are the best for you?

-Do Starbucks drinks contain too much sugar for you daily intake?

-Do the simple teas provide less sugar and fat then the signature drinks do?

-Is the Cholesterol in their drinks acceptable for regular health habits?

Our data set explores 221 different drinks with characteristics like saturated fat, caffeine, sugars, and protein percentage.

**Prerequisites**

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)

```

**Data Set**
Loading the data from the working directory, caffeine has values that varies so those data variables were excluded to get more accurate averages.
```{r, message=FALSE, warning=FALSE}
starbucks <- read.csv('../data/starbucks.csv')
```

**Data Exploration**
```{r}
summary(starbucks)
```



**Uni-variate Exploration**

Average sugar amount in grams - Everyone loves their favorite frappuccino from Starbucks until they realize its actually unhealthy, In terms of added sugars in grams frappucinos have almost double the recommended healthy amount per day of 24 grams for women and 36 grams for men.

**Sugars**
```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgsug <- mean(Sugars..g., na.rm = TRUE))
s
```
**Cholesterol**

Taking a look at the average cholesterol count in their drinks can easily contribute to early heart disease, starting your day with 42 mg of cholesterol is not a great start to your day. The recommended amount being approx 200 mg and even that isn't healthy. Even if you were to start with something like a tea drink it can contribute to long term health effects like heart disease.

```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgchol <- mean(Cholesterol..mg.))
s
  
```

**Caffeine**

Caffeine being most peoples concern when it comes to health concerns of coffee the averages stay pretty low for everything other than just their regular coffee. The average healthy adult generally is safe to consume 200 mg of caffeine a day so anything more than 1 cup a day can be unsafe. 
```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgcaf = mean(Caffeine..mg., na.rm = TRUE))
s
```

**Bi-Variate Exploration**

Looking at some characteristics comparing the "healthiest" option vs. the most unhealthy option.

**Coffee vs. Frappucino Blended Coffee**
Comparing coffee which has one of the more healthy nutritional values without addons like cream and sugar, one cup of this a day could be healthy for you as long as you aren't drinking too much due to the caffeine amounts. Then looking at the Frappucino Blended coffee which has the highest cholesterol, sugar averages across the board. It seems that one cup of coffee a day might be best and even really healthy for you compared to the special frappucinos. 

```{r}
s <- starbucks %>%
  group_by(Beverage) %>%
  filter(Beverage_category %in% c("Coffee", "Frappuccino® Blended Coffee")) %>%
  mutate(avgsug = mean(Sugars..g., na.rm = TRUE)) %>%
  mutate(avgcaf = mean(Caffeine..mg., na.rm = TRUE)) %>%
  summarise(avgcaf, avgsug)
  
s
```

**What is the best coffee**

Regular coffee with no sugar no cream can be fairly healthy for you. The different sizes can impact how many cups a day you should drink from Starbucks without reaching an unsafe caffeine limit. Short would be 2 cups, Tall would be one, grande and Venti would also be one cup a day to stay safe.
```{r}
s <- starbucks %>%
  group_by(Beverage) %>%
  filter(Beverage_category == "Coffee") %>%
  select(Caffeine..mg., Beverage_prep) 
s
```


**Data Analysis Conclusion**

Starbucks is a very popular coffee shop and I doubt one generic analysis of their products will stop people from going, however it begs the question how healthy are the other fast food drinks and foods we consume. Over the years food seems to be getting unhealthier and unhealthier even something as simple as a frappucino from Starbucks can have monumental impacts on your health in the future. Which is something to keep in mind, 


