---
title: "Final Report for Intro to Data Science"
output: html_notebook
Name: "Kyle Murphy"
---

**How healthy is Starbucks?**

**Project Author**

Kyle Murphy

**Introduction**

Starbucks has become something of a global phenomenon with how many people order Starbucks everyday. The question no one seems to be asking is what are the nutritional values of your favorite Starbucks drinks. As well as what category of Starbucks beverages are the best for you?

-Do Starbucks drinks contain too much sugar for you daily intake?

-Do the simple teas provide less sugar and fat then the signature drinks do?

-Is the caffeine and saturated fats in their drinks acceptable for regular health habits?

**Prerequisites**

```{r}
library(tidyverse)
library(dplyr)

```

**dataset**
```{r, message=FALSE, warning=FALSE}
starbucks <- read_csv("https://raw.githubusercontent.com/reisanar/datasets/master/starbucks.csv")
```

**Uni-variate Exploration**

```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgsug <- mean(`Sugars (g)`, na.rm = TRUE))
s
```




This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_