---
title: "Final Report for Intro to Data Science"
output: html_notebook
Name: "Kyle Murphy"
---

**How healthy is Starbucks?**

**Project Author**

Kyle Murphy

**Introduction**

Starbucks has become something of a global phenomenon with how many people order Starbucks everyday. The question no one seems to be asking is what are the nutritional values of your favorite Starbucks drinks. As well as what category of Starbucks beverages are the best for you?

-Do Starbucks drinks contain too much sugar for you daily intake?

-Do the simple teas provide less sugar and fat then the signature drinks do?

-Is the Cholesterol in their drinks acceptable for regular health habits?

Our data set explores 221 different drinks with characteristics like saturated fat, caffeine, sugars, and protein percentage.

**Prerequisites**

```{r}
library(tidyverse)
library(dplyr)

```

**dataset**
```{r, message=FALSE, warning=FALSE}
starbucks <- read.csv('../data/starbucks.csv')
```

**Uni-variate Exploration**

Average sugar amount in grams - Everyone loves their favorite frapp from Starbucks until they realize its actually unhealthy, In terms of added sugars in grams frappucinos have almost double the recommended healthy amount per day of 24 grams for women and 36 grams for men.

**Sugars**
```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgsug <- mean(Sugars..g., na.rm = TRUE))
s
```
**Cholesterol**

Taking a look at the average cholesterol count in their drinks can easily contribute to early heart disease, starting your day with 42 mg of cholesterol is not a great start to your day. The recommended amount being approx 200 mg and even that isn't healthy. Even if you were to start with something like a tea drink it can contribute to long term health effects like heart disease.

```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgchol <- mean(Cholesterol..mg.))
s
  
```

**Caffeine**

Caffeine being most peoples concern when it comes to health concerns of coffee the averages stay pretty low for everything other than just their regular coffee. The average healthy adult generally is safe to consume 200 mg of caffeine a day so anything more than 1 cup a day can be unsafe. 
```{r}
s <- starbucks %>%
  group_by(Beverage_category) %>%
  summarise(avgcaf <- mean(Caffeine..mg., na.rm = TRUE))
s
```




This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_